Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-26 ms.tex
reorg

\subsection{Astrophysical Signal}
We assume the measured astrophysical signal $F_\mathrm{physical}$ has the following form:
\begin{equation}
	F_\mathrm{physical}(t, \lambda) \propto F_s(\lambda) (1 + \alpha(\lambda)) \times T(t, \lambda) + F_p(t, \lambda) 
\end{equation}
where $F_s(\lambda)$ is the stellar flux as a function of wavelength, $\alpha(\lambda)$ is the additional fractional flux from the companion star, $T(t, \lambda)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), and $F_p(t, \lambda)$ is the disk-integrated planet flux. These terms are described in more detail below. We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}. The flux from the planet is given by
\begin{equation}
F_p(t) = I(t, \lambda)[R(t)]^2
\end{equation}
where $I$ is the disk-integrated planet intensity and $R$ is the planet's effective area (which changes with orbital phase due to tidal distortion).  In our final fit, we divide by the total stellar flux (primary and background stars), such that the astrophysical signal is:
\begin{equation}
	F_\mathrm{physical}(t) = T(t) + F_p(t, \lambda) /[F_s(\lambda) (1 + \alpha (\lambda))]
\end{equation}

We calculate the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}. Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$). As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets. We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.  The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.

We explored several different models for the planet's disk-integrated intensity $I(t, \lambda)$, using climate maps from the open-source Python package \texttt{SPIDERMAN} \citep{louden17}. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding planet-to-star flux for an observation at time $t$, over a specified wavelength range. We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$). These models each have different strengths. The kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.   The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate. The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis. %In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).

In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature. To address the possible effects of radius variability on our data, we predict the variation using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit). FIXME: say this doesn't matter.

FIXME: say what the dilution factor is.
%Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation. We model $E(t)$ using the analytic expression from \cite{leconte11}, which 
%FIXME doppler beaming?

@@

\subsection{Comparison of Thermal Phase Variation Models}
All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves. Table FIXME summarized the goodness of fit

>>>>

\subsection{Astrophysical Signal}
We assume the measured astrophysical signal $F_\mathrm{physical}$ has the following form:
\begin{equation}
	%F_\mathrm{physical}(\lambda, t) = F_s(\lambda) (1 + \alpha(\lambda)) \times T(\lambda, t) + F_p(\lambda, t) 
	F_\mathrm{physical}(\lambda, t) =  T(\lambda, t) + c(\lambda, t) \times F_p/F_s(\lambda, t)
\end{equation}
where $T(\lambda, t)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), $F_p/F_s(\lambda, t)$ is the disk-integrated planet-to-star flux, and $c$ is a correction factor for companion star dilution and the planet's tidal distortion.

We calculated the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}. Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$). As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets. We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.  The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.

We calculated the planet-to-star flux $F_p/F_s$ with the \texttt{SPIDERMAN} package \citep{louden17}.  This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we assumed the star is a FIXME PHOENIX model.  We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).

%We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.  (FIXME - use a PHOENIX model instead). 
We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion. The correction factor took the form: 
\begin{equation}
	c(\lambda, t) = (1 + \alpha(\lambda))A(t)
\end{equation}
where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet. We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier16}. The companion star contributes FIXME percent of the flux at FIXME $\mu$m.  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid. We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr. The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}. At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit). %FIXME: say this doesn't matter.
%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}. In the observed light curve, changes in planet radius are degenerate with changes in temperature.

%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).

%Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation. We model $E(t)$ using the analytic expression from \cite{leconte11}, which 
%FIXME doppler beaming?

@@

\subsection{Comparison of Thermal Phase Variation Models}
%These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.   The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate. The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis. %In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves. Table FIXME summarized the goodness of fit
